---
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1901
email: "jleongomez@unbosque.edu.co"
www: jdleongomez.info
orcid: 0000-0002-0092-6298
profilepic: "../images/JDL.jpg"
aboutme: |
  I am a researcher mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r Sys.setlocale('LC_TIME','English');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 207373
docname: Short Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )
library(magrittr)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()
```

# About me

\begin{minipage}[c]{0.9\linewidth}
I am an Associate Professor and Researcher at \href{https://jdleongomez.info/en/team/}{\textit{\textbf{EvoCo}: Human Behaviour and Evolution Lab}}, and leader of the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} research group (classification \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}}), \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology}, at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} in Bogota, Colombia. My research interests mostly lie in mate choice, human vocal communication, and musicality, as well as bioacoustics, psychoacoustics, and hormonal effects on human behaviour. I am very passionate about quantitative methods and \textbf{R} programming, as a tool to promote reproducibility and open science.
\end{minipage} \begin{minipage}[c]{0.1\linewidth}
\begin{flushright} 
\hfill \href{https://jdleongomez.info/en/team/}{\includegraphics[width=1.5cm, height=1.5cm]{Logo_EvoCo.png}} \newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=1.5cm, height=1.5cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (advanced: all data wrangling, analysis, plots and tables —and even this CV— made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/\href{https://rmarkdown.rstudio.com/}{R Markdown} (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5). Version control: \href{https://git-scm.com/}{Git} \faGit* and \href{https://github.com/JDLeongomez}{GitHub} \faGithub}

  \cvskill
    {Quantitative Research}
    {General and generalised models, linear mixed-effects models, multi-model inference, machine learning}

  \cvskill
    {Software}
    {\href{https://posit.co/products/open-source/rstudio/}{RStudio}, \href{https://code.visualstudio.com/}{Visual Studio Code}, \href{https://www.fon.hum.uva.nl/praat/}{Praat}, \href{https://www.audacityteam.org/}{Audacity}, \href{https://inkscape.org/}{InkScape}, \href{https://www.zotero.org/}{Zotero}}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Education

```{r education}
ezpickr::pick("../data/education_eng_S.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Working and Teaching Experience

For a full list, and a description of responsibilities, please check [my website](https://jdleongomez.info/en/profile/#experience) or my [academic CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

```{r working-experience}
ezpickr::pick("../data/working-experience_eng_S.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Accomplishments

For information on **grants**, **scholarships**, **awards** and **prizes**, please check [my website](https://jdleongomez.info/en/profile/#accomplishments) or my [academic CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

# Selected Publications

```{r scholar, echo = FALSE}
profile <- get_profile("8Q0jKHsAAAAJ")
pubs <- get_publications("8Q0jKHsAAAAJ")

h_index <- profile$h_index
g_index <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
i10_index <- profile$i10_index
pubs_num <- dim(pubs)[1]
citSum <- profile$total_cites
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=teal,
        hyperurl=https://scholar.google.com/citations?user=8Q0jKHsAAAAJ]
  
\color{white}
\begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r h_index` \end{huge}
  \begin{small} \textit{h}-index \end{small} \end{center} 
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r g_index` \end{huge}
  \begin{small} \textit{g}-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r i10_index` \end{huge}
  \begin{small} i10-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r pubs_num` \end{huge}
  \begin{small} Publications \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}  
  \begin{center} \begin{huge} `r citSum` \end{huge} 
  \begin{small} Citations \end{small} \end{center}
\end{minipage}
\end{tcolorbox}

For a full list, please check the publications section on [my website](https://jdleongomez.info/en/publication/) or my [academic CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf). 

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/featured.txt")`

\endgroup

\begin{footnotesize}
\textbf{Note:} Corresponding author in all the publications listed in this section.
\end{footnotesize}

# Investigación Abierta (YouTube channel)

\begin{minipage}[c]{0.15\linewidth}
\href{https://www.youtube.com/@InvestigacionAbierta}{\includegraphics[width=2cm, height=2cm]{Logo_IA.png}}
\end{minipage} \begin{minipage}[c]{0.85\linewidth}
\textcolor{red}{\faYoutube} \href{https://www.youtube.com/@InvestigacionAbierta}{Investigación Abierta} [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.
\end{minipage}

# Shiny Apps

\begin{minipage}[c]{0.10\linewidth}
\href{https://jdleongomez.info/en/#shiny}{\includegraphics[width=1.5cm, height=1.74cm]{shiny_hex.png}}
\end{minipage} \begin{minipage}[c]{0.90\linewidth}
I have created a few, small public apps with \href{https://shiny.posit.co/}{Shiny} in R, mostly for fun or to illustrate statistics concepts. For a list, please check \href{https://jdleongomez.info/en/#shiny}{my website}.
\end{minipage} 
# Postgraduate Supervision

For a full list, including undergraduate supervision, please check [my website](https://jdleongomez.info/en/team/) or my [academic CV](https://jdleongomez.info/en/files/jdl_cv_en.pdf).

```{r supervision}
ezpickr::pick("../data/supervision_eng_S.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Editorial Appointments

I am a [recommender](https://rr.peercommunityin.org/about/recommenders) (editor) for [PCI Registered Reports](https://rr.peercommunityin.org/) and recently acted as guest editor for a two-part theme issue on [Philosophical Transactions B](https://royalsocietypublishing.org/journal/rstb) ([Part 1](https://royalsocietypublishing.org/toc/rstb/2021/376/1840), [Part 2](https://royalsocietypublishing.org/toc/rstb/2022/377/1841)). I regularly serve as an \textit{ad-hoc} reviewer for a number of journals, such as [Proceedings of the Royal Society B: Biological Sciences](https://royalsocietypublishing.org/journal/rspb), [Royal Society Open Science](https://royalsocietypublishing.org/journal/rsos), [PLOS ONE](https://journals.plos.org/plosone/), [Evolution and Human Behavior](https://www.sciencedirect.com/journal/evolution-and-human-behavior), [Scientific Reports](https://www.nature.com/srep/), [Basic and Applied Social Psychology](https://www.tandfonline.com/toc/hbas20/current), [Cortex](https://www.journals.elsevier.com/cortex), [Perception](https://journals.sagepub.com/home/pec),
[Evolutionary Psychology](https://journals.sagepub.com/home/evp), and [Frontiers in Psychology](https://www.frontiersin.org/journals/psychology) where I am a [Review Editor](https://loop.frontiersin.org/people/438954/overview) for the [\textit{Evolutionary Psychology specialty section}](https://www.frontiersin.org/journals/psychology/sections/evolutionary-psychology).  My verified record can be viewed on my [Web of Science](https://www.webofscience.com/wos/author/record/387716) profile.
