---
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1901
email: "jleongomez@unbosque.edu.co"
www: jdleongomez.info
orcid: 0000-0002-0092-6298
profilepic: "../images/JDL.jpg"
aboutme: |
  I am a researcher mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r if (.Platform$OS.type == 'windows') { Sys.setlocale('LC_TIME','English_United Kingdom') } else { Sys.setlocale('LC_TIME','en_GB.utf8') }; format(Sys.Date(), '%d %B %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 207373
docname: Academic Curriculum Vitae
header-includes:
  - |
    \newtcolorbox{importantnote}{
      colback=gray!10,
      colframe=teal,
      boxrule=0.4pt,
      arc=2mm,
      left=3pt,
      right=3pt,
      top=3pt,
      bottom=3pt,
      enhanced,
      width=\linewidth,
    }
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

# About me

\begin{minipage}[c]{0.85\linewidth}

I am an Associate Professor and researcher at \href{https://jdleongomez.info/es/team/}{\textit{\textbf{EvoCo}: Human Behaviour and Evolution Lab}}, and leader of the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences Research Group}} (classified as \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}}), within the \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology} at the \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} in Bogotá, Colombia. I am also a founding and board member of the \textbf{\textit{Latin American Association for Human Behavioral and Evolutionary Sciences}} (\textbf{\textit{LAAHBES}}). \par \vspace{0.4em}
\textbf{Research:} My work focuses on human vocal communication, mate choice, musicality, and hormonal influences on behaviour. I have published pioneering studies on vocal modulation in social and courtship contexts. \par \vspace{0.4em}
\textbf{Open Science:} I am interested in quantitative methods and programming, especially in \textbf{R}, as tools to promote open and reproducible science. In line with these values, I serve as a \href{https://rr.peercommunityin.org/about/recommenders}{recommender} (associate editor) at \href{https://rr.peercommunityin.org/}{Peer Community In Registered Reports}.

\end{minipage} \begin{minipage}[c]{0.15\linewidth}
\begin{flushright} 
\hfill \href{https://jdleongomez.info/en/team/}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_EvoCo.png}} \newline\newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (advanced: all data wrangling, analysis, plots and tables —and even this CV— made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/\href{https://rmarkdown.rstudio.com/}{R Markdown}/\href{https://quarto.org/}{Quarto} (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5 code). Version control: \href{https://git-scm.com/}{Git} \faGit* and \href{https://github.com/JDLeongomez}{GitHub} \faGithub}

  \cvskill
    {Quantitative Research}
    {General and generalised models, linear mixed-effects models, multi-model inference, machine learning}

  \cvskill
    {Software}
    {\href{https://posit.co/products/open-source/rstudio/}{RStudio}, \href{https://code.visualstudio.com/}{Visual Studio Code}, \href{https://www.fon.hum.uva.nl/praat/}{Praat}, \href{https://www.audacityteam.org/}{Audacity}, \href{https://inkscape.org/}{InkScape}, \href{https://www.zotero.org/}{Zotero}}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Research

\begin{cvskills}
  \cvskill
    {Research Areas}
    {\textbf{Human voice • Vocal modulation • Mate choice • Human behaviour}}

  \cvskill
    {Primary Research Methods}
    {Experimental designs • Acoustic analysis • Geometric morphometrics • Stimuli rating}
\end{cvskills}

# Education

```{r education}
readxl::read_excel("../data/education_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Relevant further education

```{r edu_comp}
readxl::read_excel("../data/edu_comp_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Working Experience

```{r working-experience}
readxl::read_excel("../data/working-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Teaching Experience

```{r teaching-experience}
readxl::read_excel("../data/teaching-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Scholarships, Awards and Honors

```{r award}
readxl::read_excel("../data/award_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Grants

```{r grant}
readxl::read_excel("../data/grant_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Publications

```{r scholar, echo = FALSE}
profile <- get_profile("8Q0jKHsAAAAJ")
pubs <- get_publications("8Q0jKHsAAAAJ")

h_index <- profile$h_index
g_index <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
i10_index <- profile$i10_index
pubs_num <- dim(pubs)[1]
citSum <- profile$total_cites
meancit <- round(mean(pubs$cites), 2)
mediancit <- median(pubs$cites)
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=teal,
        hyperurl={https://scholar.google.com/citations?user=8Q0jKHsAAAAJ}]
  
\color{white}
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r h_index` \end{huge}
     \begin{small} \textit{h}-index \end{small} 
    \end{center} 
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r g_index` \end{huge}
      \begin{small} \textit{g}-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r i10_index` \end{huge}
      \begin{small} i10-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center}  
      \begin{huge} `r pubs_num` \end{huge}
      \begin{small} Publications \end{small} 
    \end{center}
  \end{minipage} 
  
  \begin{center} \noindent\line(1,0){150} Citations \noindent\line(1,0){150} \end{center}
  
  \begin{minipage}[c]{0.325\linewidth}  
    \begin{center} 
      \begin{small} Total \end{small} 
      \begin{LARGE} `r citSum` \end{LARGE} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center} 
      \begin{small} Mean \end{small} 
      \begin{LARGE} `r meancit` \end{LARGE}
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center}  
      \begin{small} Median \end{small} 
      \begin{LARGE} `r mediancit` \end{LARGE}
   \end{center}
  \end{minipage} 
\end{tcolorbox}

\begin{importantnote}
  \textcolor{teal}{\faStar} \textbf{Key authorship:} sole, first, last, or corresponding author.
\end{importantnote}

## \textbf{Editorials and Recommendations}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/recommendation.txt")`

\endgroup

\begin{minipage}[c]{0.10\linewidth}
\href{https://rr.peercommunityin.org/about/recommenders}{\includegraphics[width=1.5cm]{pci_rr.png}}
\end{minipage} \begin{minipage}[c]{0.90\linewidth}
\footnotesize{\textbf{Note:} For more information about my role as a \href{https://rr.peercommunityin.org/public/user_public_page?userId=1996}{recommender} (equivalent to Associate Editor) for \textit{Peer Community In Registered Reports}, see the section dedicated to my \hyperref[editor]{editorial roles} below.}
\end{minipage} 

## \textbf{Published Journal Articles and Works}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/journal.txt")`

\endgroup

## \textbf{Preprints and Articles under Review}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/working_paper_en.txt")`

\endgroup

# Educational Resources and Science Communication

## \textbf{Investigación Abierta (YouTube channel)}

\begin{minipage}[c]{0.15\linewidth}
\href{https://www.youtube.com/@InvestigacionAbierta}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_IA.png}}
\end{minipage} \begin{minipage}[c]{0.85\linewidth}
\textcolor{red}{\faYoutube} \href{https://www.youtube.com/@InvestigacionAbierta}{Investigación Abierta} [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.
\end{minipage}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/IA_en.txt")`

\endgroup

## \textbf{Online Practical Guides}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/guides_en.txt")`

\endgroup

## \textbf{Public Articles}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/divulgation_en.txt")`

\endgroup

## \textbf{Shiny Apps for Educational Purposes}

\begin{minipage}[c]{0.10\linewidth}
\href{https://jdleongomez.info/en/#shiny}{\includegraphics[width=1.5cm, height=1.74cm]{shiny_hex.png}}
\end{minipage} \begin{minipage}[c]{0.90\linewidth}
Developed interactive apps in R using \href{https://shiny.posit.co/}{Shiny} mainly for for teaching and illustrating statistical concepts. In this section you can find some examples.
\end{minipage} 

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/Shiny_en.txt")`

\endgroup

# Conference Presentations, Posters and Workshops

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/poster_en.txt")`

\endgroup

# Scientific Events

```{r event}
readxl::read_excel("../data/event_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Editorial Appointments {#editor}

\begin{small}
\textbf{Note:} My verified review and editor record is available from my \href{https://www.webofscience.com/wos/author/record/387716}{Web of Science} profile. 
\end{small}

```{r service}
readxl::read_excel("../data/service_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Supervision

## \textbf{Postgraduate}

The Faculty of Psychology at Universidad El Bosque does not offer research degrees, and all M-level courses are professional masters. Because of this, opportunities to supervise postgraduate students are limited, and most of my postgraduate supervision has been external.

```{r supervision}
readxl::read_excel("../data/supervision_pos_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

## \textbf{Undergraduate}

The supervised undergraduate students listed below come from different universities and academic programmes. This list only includes students for whom I was the main supervisor or who were awarded honours degrees. Additionally, I am currently supervising six students as a principal supervisor, and have supervised over 25 students as a co-supervisor.

```{r supervision-pre}
readxl::read_excel("../data/supervision_pre_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Memberships

```{r member}
readxl::read_excel("../data/member_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```