---
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1901
email: "jleongomez@unbosque.edu.co"
github: JDLeongomez
orcid: 0000-0002-0092-6298
profilepic: "../images/JDL.jpg"
aboutme: |
  I am a researcher mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r Sys.setlocale('LC_TIME','English');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 207373
docname: Academic Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )
library(magrittr)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()
```

# About me

\begin{minipage}[c]{0.85\linewidth}
I am an Associate Professor and Researcher at \href{https://jdleongomez.info/en/team/}{\textit{\textbf{EvoCo}: Human Behaviour and Evolution Lab}}, and leader of the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} research group (cassification \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}}), \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology}, at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} in Bogota, Colombia. My research interests include mate choice and human vocal communication, with an aspiration towards understanding musicality. I am also interested in bioacoustics and psychoacoustics, as well as hormonal effects on human behaviour. I published among the first articles showing within-individual changes in voice pitch in response to the social status of the listener, and have demonstrated strong effects of voice modulation on listeners in courtship contexts. I am very passionate about quantitative methods and \textbf{R} programming, as a tool to promote reproducibility and open science.
\end{minipage} \begin{minipage}[c]{0.15\linewidth}
\begin{flushright} 
\hfill \href{https://jdleongomez.info/es/team/}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_EvoCo.png}} \newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {R (advanced: all data wrangling, analysis, plots and tables -and even this CV- made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/Rmarkdown (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5)}

  \cvskill
    {Quantitative Research}
    {General and Generalised Models, Linear Mixed-effects Models, Model selection and Averaging, Machine Learning}

  \cvskill
    {Software}
    {RStudio, Visual Studio Code, Praat, Audacity, InkScape, Mendeley, Zotero}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Research

\begin{cvskills}
  \cvskill
    {Research Areas}
    {\textbf{Human voice • Vocal modulation • Mate choice • Human behaviour}}

  \cvskill
    {Primary Research Methods}
    {Experimental designs • Acoustic analysis • Geometric morphometrics • Stimuli rating}
\end{cvskills}

# Education

```{r education}
ezpickr::pick("../data/education_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Relevant further education

```{r edu_comp}
ezpickr::pick("../data/edu_comp_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Working Experience

```{r working-experience}
ezpickr::pick("../data/working-experience_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Teaching Experience

```{r teaching-experience}
ezpickr::pick("../data/teaching-experience_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Scholarships, Awards and Honors

```{r award}
ezpickr::pick("../data/award_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Grants

```{r grant}
ezpickr::pick("../data/grant_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

## \textbf{Published Journal Articles and Works}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/journal.txt")`

\endgroup

## \textbf{Preprints and Articles under Review}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/working_paper.txt")`

\endgroup

## \textbf{Science outreach}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/divulgation_en.txt")`

\endgroup

# Investigación Abierta (YouTube channel)

\begin{minipage}[c]{0.15\linewidth}
\href{https://www.youtube.com/@InvestigacionAbierta}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_IA.png}}
\end{minipage} \begin{minipage}[c]{0.85\linewidth}
\textcolor{red}{\faYoutubePlay} \href{https://www.youtube.com/@InvestigacionAbierta}{Investigación Abierta} [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.
\end{minipage}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/IA_en.txt")`

\endgroup

# Conference Presentations, Posters and Workshops

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/poster_en.txt")`

\endgroup

# Scientific Events

```{r event}
ezpickr::pick("../data/event_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Postgraduate and undergraduate Supervision

```{r supervision}
ezpickr::pick("../data/supervision_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Editorial Appointments

My verified review record is available from my [Web of Science](https://www.webofscience.com/wos/author/record/387716) profile. 

```{r service}
ezpickr::pick("../data/service_en.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Memberships

## \textbf{Current}

  * [International Society for Human Ethology (ISHE)](https://ishe.org/)

## \textbf{Past}

  * [European Human Behaviour and Evolution Association (EHBEA)](https://www.cambridge.org/core/membership/ehbea)
  * [Association for Psychological Science (APS)](https://www.psychologicalscience.org/)