---
graphics: yes
name: Juan David
surname: Leongómez
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1901
email: "jleongomez@unbosque.edu.co"
www: jdleongomez.info
orcid: 0000-0002-0092-6298
profilepic: "../images/JDL.jpg"
aboutme: |
  I am a researcher mainly interested in human behaviour, as well as quantitative methods and reproducible science.
date: "`r Sys.setlocale('LC_TIME','en_GB.utf8');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 207373
docname: Academic Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

\section{\faInfo \phantom{-} About me}

\begin{minipage}[c]{0.85\linewidth}
I am an Associate Professor and Researcher at \href{https://jdleongomez.info/en/team/}{\textit{\textbf{EvoCo}: Human Behaviour and Evolution Lab}}, and leader of the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} research group (classification \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}}), \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology}, at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} in Bogota, Colombia. My research interests mostly lie in mate choice, human vocal communication, and musicality, as well as bioacoustics, psychoacoustics, and hormonal effects on human behaviour. I published among the first articles showing within-individual changes in voice pitch in response to the social status of the listener, and have demonstrated strong effects of voice modulation on listeners in courtship contexts. I am very passionate about quantitative methods and \textbf{R} programming, as a tool to promote reproducibility and open science. Consequently, I am a \href{https://rr.peercommunityin.org/about/recommenders}{recommender} (editor) for \href{https://rr.peercommunityin.org/}{PCI Registered Reports}.
\end{minipage} \begin{minipage}[c]{0.15\linewidth}
\begin{flushright} 
\hfill \href{https://jdleongomez.info/en/team/}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_EvoCo.png}} \newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

\section{\faStar \phantom{-} Skills}

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (advanced: all data wrangling, analysis, plots and tables —and even this CV— made in R)}

  \cvskill
    {Reproducible Reports}
    {Markdown/\href{https://rmarkdown.rstudio.com/}{R Markdown} (including {\fontfamily{cmr}\selectfont\LaTeX} and HTML\faHtml5). Version control: \href{https://git-scm.com/}{Git} \faGit* and \href{https://github.com/JDLeongomez}{GitHub} \faGithub}

  \cvskill
    {Quantitative Research}
    {General and generalised models, linear mixed-effects models, multi-model inference, machine learning}

  \cvskill
    {Software}
    {\href{https://posit.co/products/open-source/rstudio/}{RStudio}, \href{https://code.visualstudio.com/}{Visual Studio Code}, \href{https://www.fon.hum.uva.nl/praat/}{Praat}, \href{https://www.audacityteam.org/}{Audacity}, \href{https://inkscape.org/}{InkScape}, \href{https://www.zotero.org/}{Zotero}}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

\section{\faGlasses \phantom{-} Research}

\begin{cvskills}
  \cvskill
    {Research Areas}
    {\textbf{Human voice • Vocal modulation • Mate choice • Human behaviour}}

  \cvskill
    {Primary Research Methods}
    {Experimental designs • Acoustic analysis • Geometric morphometrics • Stimuli rating}
\end{cvskills}

\section{\faGraduationCap \phantom{-} Education}

```{r education}
readxl::read_excel("../data/education_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faChalkboard \phantom{-} Relevant further education}

```{r edu_comp}
readxl::read_excel("../data/edu_comp_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faBriefcase \phantom{-} Working Experience}

```{r working-experience}
readxl::read_excel("../data/working-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faUniversity \phantom{-} Teaching Experience}

```{r teaching-experience}
readxl::read_excel("../data/teaching-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faAward \phantom{-} Scholarships, Awards and Honors}

```{r award}
readxl::read_excel("../data/award_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faMoneyBill \phantom{-} Grants}

```{r grant}
readxl::read_excel("../data/grant_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faBookOpen \phantom{-} Publications}

```{r scholar, echo = FALSE}
profile <- get_profile("8Q0jKHsAAAAJ")
pubs <- get_publications("8Q0jKHsAAAAJ")

h_index <- profile$h_index
g_index <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
i10_index <- profile$i10_index
pubs_num <- dim(pubs)[1]
citSum <- profile$total_cites
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=teal,
        hyperurl={https://scholar.google.com/citations?user=8Q0jKHsAAAAJ}]
  
\color{white}
\begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r h_index` \end{huge}
  \begin{small} \textit{h}-index \end{small} \end{center} 
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r g_index` \end{huge}
  \begin{small} \textit{g}-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r i10_index` \end{huge}
  \begin{small} i10-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r pubs_num` \end{huge}
  \begin{small} Publications \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}  
  \begin{center} \begin{huge} `r citSum` \end{huge} 
  \begin{small} Citations \end{small} \end{center}
\end{minipage}
\end{tcolorbox}

## \textbf{Published Journal Articles and Works}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/journal.txt")`

\endgroup

## \textbf{Preprints and Articles under Review}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/working_paper.txt")`

\endgroup

## \textbf{Science outreach}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/divulgation_en.txt")`

\endgroup

\section{\faVideo \phantom{-} Investigación Abierta (YouTube channel)}

\begin{minipage}[c]{0.15\linewidth}
\href{https://www.youtube.com/@InvestigacionAbierta}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_IA.png}}
\end{minipage} \begin{minipage}[c]{0.85\linewidth}
\textcolor{red}{\faYoutube} \href{https://www.youtube.com/@InvestigacionAbierta}{Investigación Abierta} [\textit{Open Research}] is a YouTube channel (in Spanish) where I post videos and tutorials related to quantitative research methods and open science, as well as useful open source software.
\end{minipage}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/IA_en.txt")`

\endgroup

\section{\faCode \phantom{-} Shiny Apps}

\begin{minipage}[c]{0.10\linewidth}
\href{https://jdleongomez.info/en/#shiny}{\includegraphics[width=1.5cm, height=1.74cm]{shiny_hex.png}}
\end{minipage} \begin{minipage}[c]{0.90\linewidth}
I have created a few, small public apps with \href{https://shiny.posit.co/}{Shiny} in R, mostly for fun. While I am still learning, in this section there are some examples.
\end{minipage} 

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/Shiny_en.txt")`

\endgroup

\section{\faChalkboardTeacher \phantom{-} Conference Presentations, Posters and Workshops}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/poster_en.txt")`

\endgroup

\section{\faUsers \phantom{-} Scientific Events}

```{r event}
readxl::read_excel("../data/event_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faUserEdit \phantom{-} Editorial Appointments}

\begin{small}
\textbf{Note:} My verified review and editor record is available from my \href{https://www.webofscience.com/wos/author/record/387716}{Web of Science} profile. 
\end{small}

```{r service}
readxl::read_excel("../data/service_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faUserGraduate \phantom{-} Research Supervision}

## \textbf{Postgraduate}

The Faculty of Psychology at Universidad El Bosque does not offer research degrees, and all M-level courses are professional masters. Because of this, opportunities to supervise postgraduate students are limited, and most of my postgraduate supervision has been external.

```{r supervision}
readxl::read_excel("../data/supervision_pos_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

## \textbf{Undergraduate}

The supervised undergraduate students listed below come from different universities and academic programmes. This list only includes students for whom I was the main supervisor or who were awarded honours degrees. Additionally, I am currently supervising six students as a principal supervisor, and have supervised over 25 students as a co-supervisor.

```{r supervision-pre}
readxl::read_excel("../data/supervision_pre_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

\section{\faIdCard \phantom{-} Memberships}

```{r member}
readxl::read_excel("../data/member_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```