---
graphics: yes
name: Juan David
surname: Leongómez Peña
position: Profesor Asociado
address: "PhD University of Stirling · MSc University of Liverpool"
phone: (+57) 319 407 7102
email: "juanleongomez@gmail.com"
www: jdleongomez.info
date: "`r Sys.setlocale('LC_TIME','Spanish');format(Sys.Date(),'%d de %B de %Y')`"
headcolor: 333333
docname: Cursos y su justificación
bibliography: referencias.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

\vspace{4mm}
\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=black]
  
\color{white}
\begin{LARGE}\begin{center}
Documento 2. \textbf{Cursos y su justificación}
\end{center}\end{LARGE}
\end{tcolorbox}

```{r}
options(knitr.kable.NA = "")
readxl::read_excel("Tabla cursos.xlsx")  |>
  tidyr::fill() |> 
  kable(align = "ccl",
        linesep = "",
        col.names = c("Curso", 
                      "Nivel",
                      "Justificación (a partir de su experiencia o formación académica)"),
        escape = FALSE) |> 
  kable_styling(font_size = 8, latex_options = c("hold_position")) |>
  column_spec(3, width = "40em", border_right = TRUE) |> 
  column_spec(2, width = "6em") |>
  column_spec(1, width = "10em", border_left = TRUE) |> 
  row_spec(c(2,4,6,8,10:12), hline_after = TRUE) |> 
  row_spec(11:13, background = "lightgray2") |>
  row_spec(0, bold = TRUE, italic = TRUE, font_size = 11, align = "c") |> 
  pack_rows("Cursos no electivos", 1, 10) |>
  pack_rows("Otros cursos", 11, 13,  latex_gap_space = "3em",)
```

\newpage

# Referencias

\begin{multicols}{2}
\AtNextBibliography{\footnotesize}
\printbibliography[heading=none]
\end{multicols}

\def\printbibliography{}